Generating Random Logic Programs Using Constraint Programming

### 2020-01-22 paper/impact.tex
Writing about the experiments

% Created by tikzDevice version 0.12.3 on 2020-01-21 14:48:17
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (234.88,176.16);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (234.88,176.16);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (234.88,176.16);
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 25.78, 19.53) rectangle (231.38,172.66);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.78, 51.08) --
	(231.38, 51.08);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.78,102.07) --
	(231.38,102.07);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.78,153.07) --
	(231.38,153.07);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 63.26, 19.53) --
	( 63.26,172.66);

\path[draw=drawColor,line width= 0.2pt,line join=round] (119.52, 19.53) --
	(119.52,172.66);

\path[draw=drawColor,line width= 0.2pt,line join=round] (175.79, 19.53) --
	(175.79,172.66);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.78, 25.58) --
	(231.38, 25.58);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.78, 76.58) --
	(231.38, 76.58);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.78,127.57) --
	(231.38,127.57);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.12, 19.53) --
	( 35.12,172.66);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 91.39, 19.53) --
	( 91.39,172.66);

\path[draw=drawColor,line width= 0.4pt,line join=round] (147.65, 19.53) --
	(147.65,172.66);

\path[draw=drawColor,line width= 0.4pt,line join=round] (203.92, 19.53) --
	(203.92,172.66);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 26.49) --
	( 91.39, 27.97) --
	(147.65, 34.12) --
	(203.92, 77.20);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 58.87) --
	( 91.39, 62.68) --
	(124.30, 68.55) --
	(147.65, 72.47);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 60.44) --
	( 91.39, 64.58) --
	(147.65, 66.81) --
	(203.92, 70.73);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 62.87) --
	( 91.39, 64.62) --
	(147.65, 67.25) --
	(203.92, 67.83);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 58.10) --
	( 91.39, 59.23) --
	(147.65, 65.57) --
	(203.92, 79.66);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 30.36) --
	( 91.39, 30.94) --
	(147.65, 35.55) --
	(203.92,165.70);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor,fill opacity=0.75] ( 32.63, 23.99) --
	( 37.62, 23.99) --
	( 37.62, 28.99) --
	( 32.63, 28.99) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] ( 88.89, 25.47) --
	( 93.89, 25.47) --
	( 93.89, 30.46) --
	( 88.89, 30.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (145.16, 31.63) --
	(150.15, 31.63) --
	(150.15, 36.62) --
	(145.16, 36.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (201.42, 74.70) --
	(206.42, 74.70) --
	(206.42, 79.69) --
	(201.42, 79.69) --
	cycle;
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor,fill opacity=0.75] ( 35.12, 58.87) circle (  2.50);

\path[fill=fillColor,fill opacity=0.75] ( 91.39, 62.68) circle (  2.50);

\path[fill=fillColor,fill opacity=0.75] (124.30, 68.55) circle (  2.50);

\path[fill=fillColor,fill opacity=0.75] (147.65, 72.47) circle (  2.50);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor,fill opacity=0.75] ( 35.12, 64.32) --
	( 38.49, 58.50) --
	( 31.76, 58.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] ( 91.39, 68.46) --
	( 94.75, 62.64) --
	( 88.03, 62.64) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (147.65, 70.70) --
	(151.02, 64.87) --
	(144.29, 64.87) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (203.92, 74.62) --
	(207.28, 68.79) --
	(200.56, 68.79) --
	cycle;
\definecolor{fillColor}{RGB}{231,41,138}

\path[fill=fillColor,fill opacity=0.75] ( 32.63, 62.87) --
	( 35.12, 65.37) --
	( 37.62, 62.87) --
	( 35.12, 60.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] ( 88.89, 64.62) --
	( 91.39, 67.11) --
	( 93.89, 64.62) --
	( 91.39, 62.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (145.16, 67.25) --
	(147.65, 69.74) --
	(150.15, 67.25) --
	(147.65, 64.75) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (201.42, 67.83) --
	(203.92, 70.32) --
	(206.42, 67.83) --
	(203.92, 65.33) --
	cycle;
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 35.12, 58.10) circle (  2.50);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 91.39, 59.23) circle (  2.50);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (147.65, 65.57) circle (  2.50);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (203.92, 79.66) circle (  2.50);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 35.12, 30.36) circle (  1.67);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 91.39, 30.94) circle (  1.67);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (147.65, 35.55) circle (  1.67);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (203.92,165.70) circle (  1.67);
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);

\path[] (216.56, 79.75) -- (203.92, 77.20);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (218.37, 74.87) --
	(228.37, 74.87) --
	(228.29, 74.88) --
	(228.58, 74.89) --
	(228.87, 74.94) --
	(229.14, 75.05) --
	(229.39, 75.19) --
	(229.62, 75.38) --
	(229.81, 75.60) --
	(229.97, 75.84) --
	(230.08, 76.11) --
	(230.15, 76.39) --
	(230.17, 76.68) --
	(230.17, 76.68) --
	(230.17, 83.01) --
	(230.17, 83.01) --
	(230.15, 83.30) --
	(230.08, 83.58) --
	(229.97, 83.85) --
	(229.81, 84.09) --
	(229.62, 84.31) --
	(229.39, 84.50) --
	(229.14, 84.64) --
	(228.87, 84.74) --
	(228.58, 84.80) --
	(228.37, 84.82) --
	(218.37, 84.82) --
	(218.59, 84.80) --
	(218.30, 84.81) --
	(218.01, 84.78) --
	(217.73, 84.70) --
	(217.47, 84.57) --
	(217.23, 84.41) --
	(217.02, 84.21) --
	(216.84, 83.97) --
	(216.71, 83.72) --
	(216.61, 83.44) --
	(216.57, 83.15) --
	(216.56, 83.01) --
	(216.56, 76.68) --
	(216.57, 76.83) --
	(216.57, 76.54) --
	(216.61, 76.25) --
	(216.71, 75.97) --
	(216.84, 75.71) --
	(217.02, 75.48) --
	(217.23, 75.28) --
	(217.47, 75.12) --
	(217.73, 74.99) --
	(218.01, 74.91) --
	(218.30, 74.88) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
\definecolor{drawColor}{RGB}{27,158,119}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (223.37, 77.88) {$|\mathcal{P}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);

\path[] (217.03, 67.65) -- (203.92, 70.73);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (218.84, 62.52) --
	(228.37, 62.52) --
	(228.29, 62.52) --
	(228.58, 62.53) --
	(228.87, 62.59) --
	(229.14, 62.69) --
	(229.39, 62.84) --
	(229.62, 63.02) --
	(229.81, 63.24) --
	(229.97, 63.48) --
	(230.08, 63.75) --
	(230.15, 64.03) --
	(230.17, 64.32) --
	(230.17, 64.32) --
	(230.17, 70.65) --
	(230.17, 70.65) --
	(230.15, 70.94) --
	(230.08, 71.22) --
	(229.97, 71.49) --
	(229.81, 71.74) --
	(229.62, 71.95) --
	(229.39, 72.14) --
	(229.14, 72.28) --
	(228.87, 72.39) --
	(228.58, 72.44) --
	(228.37, 72.46) --
	(218.84, 72.46) --
	(219.06, 72.44) --
	(218.77, 72.46) --
	(218.48, 72.42) --
	(218.20, 72.34) --
	(217.94, 72.22) --
	(217.70, 72.05) --
	(217.49, 71.85) --
	(217.31, 71.62) --
	(217.18, 71.36) --
	(217.09, 71.08) --
	(217.04, 70.80) --
	(217.03, 70.65) --
	(217.03, 64.32) --
	(217.04, 64.47) --
	(217.04, 64.18) --
	(217.09, 63.89) --
	(217.18, 63.61) --
	(217.31, 63.36) --
	(217.49, 63.12) --
	(217.70, 62.92) --
	(217.94, 62.76) --
	(218.20, 62.63) --
	(218.48, 62.55) --
	(218.77, 62.52) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
\definecolor{drawColor}{RGB}{117,112,179}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (223.60, 65.53) {$|\mathcal{V}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);

\path[] (217.66, 56.17) -- (203.92, 67.83);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (219.47, 50.14) --
	(228.37, 50.14) --
	(228.29, 50.14) --
	(228.58, 50.15) --
	(228.87, 50.21) --
	(229.14, 50.31) --
	(229.39, 50.46) --
	(229.62, 50.64) --
	(229.81, 50.86) --
	(229.97, 51.11) --
	(230.08, 51.37) --
	(230.15, 51.66) --
	(230.17, 51.95) --
	(230.17, 51.95) --
	(230.17, 58.27) --
	(230.17, 58.27) --
	(230.15, 58.56) --
	(230.08, 58.85) --
	(229.97, 59.11) --
	(229.81, 59.36) --
	(229.62, 59.58) --
	(229.39, 59.76) --
	(229.14, 59.91) --
	(228.87, 60.01) --
	(228.58, 60.07) --
	(228.37, 60.08) --
	(219.47, 60.08) --
	(219.68, 60.07) --
	(219.39, 60.08) --
	(219.11, 60.04) --
	(218.83, 59.96) --
	(218.56, 59.84) --
	(218.32, 59.67) --
	(218.11, 59.47) --
	(217.94, 59.24) --
	(217.80, 58.98) --
	(217.71, 58.71) --
	(217.67, 58.42) --
	(217.66, 58.27) --
	(217.66, 51.95) --
	(217.67, 52.09) --
	(217.67, 51.80) --
	(217.71, 51.51) --
	(217.80, 51.24) --
	(217.94, 50.98) --
	(218.11, 50.75) --
	(218.32, 50.55) --
	(218.56, 50.38) --
	(218.83, 50.26) --
	(219.11, 50.18) --
	(219.39, 50.14) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
\definecolor{drawColor}{RGB}{231,41,138}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (223.92, 53.15) {$|\mathcal{C}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);

\path[] (206.06, 87.23) -- (203.92, 79.66);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (192.74, 87.23) --
	(219.48, 87.23) --
	(219.40, 87.23) --
	(219.70, 87.24) --
	(219.98, 87.30) --
	(220.25, 87.40) --
	(220.50, 87.54) --
	(220.73, 87.73) --
	(220.92, 87.95) --
	(221.08, 88.19) --
	(221.19, 88.46) --
	(221.26, 88.74) --
	(221.28, 89.03) --
	(221.28, 89.03) --
	(221.28, 95.36) --
	(221.28, 95.36) --
	(221.26, 95.65) --
	(221.19, 95.93) --
	(221.08, 96.20) --
	(220.92, 96.45) --
	(220.73, 96.66) --
	(220.50, 96.85) --
	(220.25, 96.99) --
	(219.98, 97.10) --
	(219.70, 97.15) --
	(219.48, 97.17) --
	(192.74, 97.17) --
	(192.95, 97.15) --
	(192.66, 97.17) --
	(192.37, 97.13) --
	(192.10, 97.05) --
	(191.83, 96.93) --
	(191.59, 96.76) --
	(191.38, 96.56) --
	(191.21, 96.33) --
	(191.07, 96.07) --
	(190.98, 95.79) --
	(190.94, 95.51) --
	(190.93, 95.36) --
	(190.93, 89.03) --
	(190.94, 89.18) --
	(190.94, 88.89) --
	(190.98, 88.60) --
	(191.07, 88.32) --
	(191.21, 88.07) --
	(191.38, 87.83) --
	(191.59, 87.63) --
	(191.83, 87.47) --
	(192.10, 87.34) --
	(192.37, 87.26) --
	(192.66, 87.23) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
\definecolor{drawColor}{RGB}{102,166,30}

>>>>

% Created by tikzDevice version 0.12.3 on 2020-01-22 11:34:15
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (216.81,176.16);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (216.81,176.16);
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.78, 51.08) --
	(213.31, 51.08);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.78,102.07) --
	(213.31,102.07);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.78,153.07) --
	(213.31,153.07);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 59.96, 19.53) --
	( 59.96,172.66);

\path[draw=drawColor,line width= 0.2pt,line join=round] (111.28, 19.53) --
	(111.28,172.66);

\path[draw=drawColor,line width= 0.2pt,line join=round] (162.60, 19.53) --
	(162.60,172.66);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.78, 25.58) --
	(213.31, 25.58);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.78, 76.58) --
	(213.31, 76.58);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.78,127.57) --
	(213.31,127.57);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 34.30, 19.53) --
	( 34.30,172.66);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 85.62, 19.53) --
	( 85.62,172.66);

\path[draw=drawColor,line width= 0.4pt,line join=round] (136.94, 19.53) --
	(136.94,172.66);

\path[draw=drawColor,line width= 0.4pt,line join=round] (188.26, 19.53) --
	(188.26,172.66);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 26.49) --
	( 85.62, 27.97) --
	(136.94, 34.12) --
	(188.26, 77.20);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 58.87) --
	( 85.62, 62.68) --
	(115.64, 68.55) --
	(136.94, 72.47);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 60.44) --
	( 85.62, 64.58) --
	(136.94, 66.81) --
	(188.26, 70.73);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 62.87) --
	( 85.62, 64.62) --
	(136.94, 67.25) --
	(188.26, 67.83);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 58.10) --
	( 85.62, 59.23) --
	(136.94, 65.57) --
	(188.26, 79.66);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 30.36) --
	( 85.62, 30.94) --
	(136.94, 35.55) --
	(188.26,165.70);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor,fill opacity=0.75] ( 31.81, 23.99) --
	( 36.80, 23.99) --
	( 36.80, 28.99) --
	( 31.81, 28.99) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] ( 83.13, 25.47) --
	( 88.12, 25.47) --
	( 88.12, 30.46) --
	( 83.13, 30.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (134.45, 31.63) --
	(139.44, 31.63) --
	(139.44, 36.62) --
	(134.45, 36.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (185.77, 74.70) --
	(190.76, 74.70) --
	(190.76, 79.69) --
	(185.77, 79.69) --
	cycle;
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor,fill opacity=0.75] ( 34.30, 58.87) circle (  2.50);

\path[fill=fillColor,fill opacity=0.75] ( 85.62, 62.68) circle (  2.50);

\path[fill=fillColor,fill opacity=0.75] (115.64, 68.55) circle (  2.50);

\path[fill=fillColor,fill opacity=0.75] (136.94, 72.47) circle (  2.50);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor,fill opacity=0.75] ( 34.30, 64.32) --
	( 37.67, 58.50) --
	( 30.94, 58.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] ( 85.62, 68.46) --
	( 88.99, 62.64) --
	( 82.26, 62.64) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (136.94, 70.70) --
	(140.31, 64.87) --
	(133.58, 64.87) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (188.26, 74.62) --
	(191.63, 68.79) --
	(184.90, 68.79) --
	cycle;
\definecolor{fillColor}{RGB}{231,41,138}

\path[fill=fillColor,fill opacity=0.75] ( 31.81, 62.87) --
	( 34.30, 65.37) --
	( 36.80, 62.87) --
	( 34.30, 60.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] ( 83.13, 64.62) --
	( 85.62, 67.11) --
	( 88.12, 64.62) --
	( 85.62, 62.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (134.45, 67.25) --
	(136.94, 69.74) --
	(139.44, 67.25) --
	(136.94, 64.75) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (185.77, 67.83) --
	(188.26, 70.32) --
	(190.76, 67.83) --
	(188.26, 65.33) --
	cycle;
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 34.30, 58.10) circle (  2.50);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 85.62, 59.23) circle (  2.50);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (136.94, 65.57) circle (  2.50);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (188.26, 79.66) circle (  2.50);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 34.30, 30.36) circle (  1.67);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 85.62, 30.94) circle (  1.67);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (136.94, 35.55) circle (  1.67);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (188.26,165.70) circle (  1.67);
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);

\path[] (198.49, 79.68) -- (188.26, 77.20);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (200.30, 74.83) --
	(210.30, 74.83) --
	(210.23, 74.83) --
	(210.52, 74.84) --
	(210.80, 74.90) --
	(211.07, 75.00) --
	(211.33, 75.15) --
	(211.55, 75.33) --
	(211.74, 75.55) --
	(211.90, 75.80) --
	(212.01, 76.06) --
	(212.08, 76.35) --
	(212.11, 76.63) --
	(212.11, 76.63) --
	(212.11, 82.96) --
	(212.11, 82.96) --
	(212.08, 83.25) --
	(212.01, 83.54) --
	(211.90, 83.80) --
	(211.74, 84.05) --
	(211.55, 84.27) --
	(211.33, 84.45) --
	(211.07, 84.60) --
	(210.80, 84.70) --
	(210.52, 84.76) --
	(210.30, 84.77) --
	(200.30, 84.77) --
	(200.52, 84.76) --
	(200.23, 84.77) --
	(199.94, 84.73) --
	(199.66, 84.65) --
	(199.40, 84.53) --
	(199.16, 84.36) --
	(198.95, 84.16) --
	(198.77, 83.93) --
	(198.64, 83.67) --
	(198.55, 83.40) --
	(198.50, 83.11) --
	(198.49, 82.96) --
	(198.49, 76.63) --
	(198.50, 76.78) --
	(198.50, 76.49) --
	(198.55, 76.20) --
	(198.64, 75.93) --
	(198.77, 75.67) --
	(198.95, 75.44) --
	(199.16, 75.24) --
	(199.40, 75.07) --
	(199.66, 74.95) --
	(199.94, 74.86) --
	(200.23, 74.83) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{27,158,119}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.30, 77.84) {$|\mathcal{P}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);

\path[] (198.97, 67.62) -- (188.26, 70.73);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (200.77, 62.43) --
	(210.30, 62.43) --
	(210.23, 62.43) --
	(210.52, 62.44) --
	(210.80, 62.50) --
	(211.07, 62.60) --
	(211.33, 62.75) --
	(211.55, 62.93) --
	(211.74, 63.15) --
	(211.90, 63.39) --
	(212.01, 63.66) --
	(212.08, 63.94) --
	(212.11, 64.23) --
	(212.11, 64.23) --
	(212.11, 70.56) --
	(212.11, 70.56) --
	(212.08, 70.85) --
	(212.01, 71.13) --
	(211.90, 71.40) --
	(211.74, 71.65) --
	(211.55, 71.87) --
	(211.33, 72.05) --
	(211.07, 72.19) --
	(210.80, 72.30) --
	(210.52, 72.36) --
	(210.30, 72.37) --
	(200.77, 72.37) --
	(200.99, 72.36) --
	(200.70, 72.37) --
	(200.41, 72.33) --
	(200.13, 72.25) --
	(199.87, 72.13) --
	(199.63, 71.96) --
	(199.42, 71.76) --
	(199.25, 71.53) --
	(199.11, 71.27) --
	(199.02, 71.00) --
	(198.97, 70.71) --
	(198.97, 70.56) --
	(198.97, 64.23) --
	(198.97, 64.38) --
	(198.97, 64.09) --
	(199.02, 63.80) --
	(199.11, 63.53) --
	(199.25, 63.27) --
	(199.42, 63.04) --
	(199.63, 62.83) --
	(199.87, 62.67) --
	(200.13, 62.54) --
	(200.41, 62.46) --
	(200.70, 62.43) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{117,112,179}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.54, 65.44) {$|\mathcal{V}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);

\path[] (199.59, 56.21) -- (188.26, 67.83);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (201.40, 50.08) --
	(210.30, 50.08) --
	(210.23, 50.08) --
	(210.52, 50.10) --
	(210.80, 50.15) --
	(211.07, 50.26) --
	(211.33, 50.40) --
	(211.55, 50.59) --
	(211.74, 50.80) --
	(211.90, 51.05) --
	(212.01, 51.32) --
	(212.08, 51.60) --
	(212.11, 51.89) --
	(212.11, 51.89) --
	(212.11, 58.22) --
	(212.11, 58.22) --
	(212.08, 58.51) --
	(212.01, 58.79) --
	(211.90, 59.06) --
	(211.74, 59.30) --
	(211.55, 59.52) --
	(211.33, 59.71) --
	(211.07, 59.85) --
	(210.80, 59.95) --
	(210.52, 60.01) --
	(210.30, 60.02) --
	(201.40, 60.02) --
	(201.62, 60.01) --
	(201.33, 60.02) --
	(201.04, 59.99) --
	(200.76, 59.91) --
	(200.50, 59.78) --
	(200.26, 59.62) --
	(200.05, 59.42) --
	(199.87, 59.18) --
	(199.74, 58.93) --
	(199.65, 58.65) --
	(199.60, 58.36) --
	(199.59, 58.22) --
	(199.59, 51.89) --
	(199.60, 52.03) --
	(199.60, 51.74) --
	(199.65, 51.46) --
	(199.74, 51.18) --
	(199.87, 50.92) --
	(200.05, 50.69) --
	(200.26, 50.49) --
	(200.50, 50.32) --
	(200.76, 50.20) --
	(201.04, 50.12) --
	(201.33, 50.08) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{231,41,138}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.85, 53.09) {$|\mathcal{C}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);

\path[] (189.92, 87.17) -- (188.26, 79.66);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (176.58, 87.17) --
	(203.32, 87.17) --
	(203.24, 87.17) --
	(203.53, 87.19) --
	(203.82, 87.24) --
	(204.09, 87.35) --
	(204.34, 87.49) --
	(204.57, 87.68) --
	(204.76, 87.89) --
	(204.92, 88.14) --
	(205.03, 88.41) --
	(205.10, 88.69) --
	(205.12, 88.98) --
	(205.12, 88.98) --
	(205.12, 95.31) --
	(205.12, 95.31) --
	(205.10, 95.60) --
	(205.03, 95.88) --
	(204.92, 96.15) --
	(204.76, 96.39) --
	(204.57, 96.61) --
	(204.34, 96.79) --
	(204.09, 96.94) --
	(203.82, 97.04) --
	(203.53, 97.10) --
	(203.32, 97.11) --
	(176.58, 97.11) --
	(176.79, 97.10) --
	(176.50, 97.11) --
	(176.21, 97.08) --
	(175.93, 97.00) --
	(175.67, 96.87) --
	(175.43, 96.71) --
	(175.22, 96.51) --
	(175.05, 96.27) --
	(174.91, 96.02) --
	(174.82, 95.74) --
	(174.77, 95.45) --
	(174.77, 95.31) --
	(174.77, 88.98) --
	(174.77, 89.12) --
	(174.77, 88.83) --
	(174.82, 88.55) --
	(174.91, 88.27) --
	(175.05, 88.01) --
	(175.22, 87.78) --
	(175.43, 87.58) --
	(175.67, 87.41) --
	(175.93, 87.29) --
	(176.21, 87.21) --
	(176.50, 87.17) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{102,166,30}
